### 2025-08-16 chapters/benchmark.tex
introduced latex diagrams

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/kyber_64M_1Core.pdf}
    \caption{Comparison of Kyber Median CPU Cycles per Operation: Sequential Single-Threaded (\texttt{run10\_SEQ}) vs Parallel Merged (\texttt{run10}) Execution (10 Runs)}
    \label{fig:kyber_native_cycles}
\end{figure}
All cryptographic operations executed entirely in user space, without invoking privileged instructions or incurring system-level overhead. Memory footprint remained minimal (peak RSS ~10~KB), with only a single minor page fault observed across all runs.

\begin{table}[h]
\centering
\scriptsize
\begin{tabular}{|l|r|r|p{4.5cm}|}
\hline
\textbf{Operation} & \textbf{Parallel Run10 Median (cycles)} & \textbf{Sequential Run10 Median (cycles)} & \textbf{Rationale / Notes} \\
\hline
indcpa\_keypair & 1,870,200 & 1,702,800 & Baseline IND-CPA key generation cost for setting up public/private pairs. \\
\hline
indcpa\_enc     & 38,376,800 & 2,174,400 & Parallel vs sequential encryption overhead comparison. \\
\hline
indcpa\_dec     & 39,060,800 & 618,400   & Decryption efficiency gap between modes. \\
\hline
kyber\_keypair  & 1,870,200 & 1,800,300 & Full Kyber keypair generation timing. \\
\hline
kyber\_encaps   & 38,376,800 & 2,285,900 & Encapsulation performance with shared secret derivation. \\
\hline
kyber\_decaps   & 39,060,800 & 2,921,800 & Decapsulation latency and handshake completion time. \\
\hline
\end{tabular}
\caption{Median CPU cycles for Kyber operations with concise context to fit page width.}
\label{tab:kyber_median_cycles}
\end{table}

@@

%\begin{figure}[h]
%    \centering
%    \includegraphics[width=0.7\textwidth]{figures/wall_clock_comparison.pdf}
%    \caption{Wall-clock execution time across benchmarks (native vs enclave, averaged over 10 runs).}
%    \label{fig:wall_clock}
%\end{figure}

@@

% \begin{figure}[htbp]
%   \centering
%   \includegraphics[width=0.75\linewidth]{figures/enclave_memory_pagefaults.png}
%   \caption{Resident Set Size (RSS) memory usage and page fault counts during Kyber enclave runs, showing stable memory consumption and minimal paging overhead.}
%   \label{fig:memory_pagefaults}
% \end{figure}

@@

% \begin{figure}[htbp]
%   \centering
%   \includegraphics[width=0.75\linewidth]{figures/context_switches_comparison.png}
%   \caption{Involuntary context switches during native versus enclave execution, highlighting a nearly 200$\times$ increase under enclave protection.}
%   \label{fig:context_switches}
% \end{figure}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|p{3.5cm}|}
\hline
\textbf{Benchmark} & \textbf{Native Time (s)} & \textbf{Enclave Time (s)} & \textbf{Overhead Factor} & \textbf{Involuntary CS} \\
\hline
Kyber     & 10.7   & 29.2   & 2.73$\times$  & 66,000 \\
\hline
Dhrystone & 15.3   & 24.7   & 1.61$\times$  & 66,000 \\
\hline
CoreMark  & 101.5  & 107.3  & 1.06$\times$  & 66,000 \\
\hline
\end{tabular}
\caption{Enclave Execution Sensitivity Across Workloads. Overhead factors indicate slowdown relative to native execution.}
\label{tab:sensitivity-overheads}
\end{table}

>>>>

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/kyber_64M_1Core.pdf}
    \caption{Comparison of Kyber Median CPU Cycles per Operation: Sequential Single-Threaded (\texttt{run10\_SEQ}) vs Parallel Merged (\texttt{run10}) Execution (10 Runs)}
    \label{fig:kyber_native_cycles}
\end{figure}

All cryptographic operations executed entirely in user space, without invoking privileged instructions or incurring system-level overhead. Memory footprint remained minimal (peak RSS ~10~KB), with only a single minor page fault observed across all runs.

\begin{figure}[h]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=10pt,
    width=14cm,
    height=8cm,
    ymode=log,
    log origin=infty,
    ymin=1e5,
    ymax=1e9,
    ytick={1e5,1e6,1e7,1e8,1e9},
    yticklabels={10$^5$,10$^6$,10$^7$,10$^8$,10$^9$},
    ylabel={Median CPU Cycles (log scale)},
    symbolic x coords={
        indcpa\_keypair,
        indcpa\_enc,
        indcpa\_dec,
        kyber\_keypair,
        kyber\_encaps,
        kyber\_decaps
    },
    xtick=data,
    x tick label style={rotate=30, anchor=east},
    enlarge x limits=0.05,
    ymajorgrids,
    grid style=dashed,
    legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1},
    nodes near coords,
    every node near coord/.append style={font=\scriptsize, rotate=90, anchor=west}
]
% Parallel values
\addplot[pattern=north east lines,pattern color=black] coordinates {
    (indcpa\_keypair,1870200)
    (indcpa\_enc,38376800)
    (indcpa\_dec,39060800)
    (kyber\_keypair,1870200)
    (kyber\_encaps,38376800)
    (kyber\_decaps,39060800)
};
% Sequential values
\addplot[pattern=dots,pattern color=black] coordinates {
    (indcpa\_keypair,1702800)
    (indcpa\_enc,2174400)
    (indcpa\_dec,618400)
    (kyber\_keypair,1800300)
    (kyber\_encaps,2285900)
    (kyber\_decaps,2921800)
};

\legend{Parallel, Sequential}
\end{axis}
\end{tikzpicture}
\caption{Median CPU cycles for Kyber operations in parallel vs sequential modes, plotted on a logarithmic scale to make smaller values visible alongside large ones.}
\label{fig:kyber_median_cycles_chart_log}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}

% --- Left axis: Times + slowdown factors ---
\begin{axis}[
    ybar,
    bar width=8pt,
    width=14cm,
    height=8cm,
    ymin=0,
    ymax=120,
    ylabel={Time (s) / Slowdown ×},
    symbolic x coords={Kyber,Dhrystone,CoreMark},
    xtick=data,
    enlarge x limits=0.35,
    ymajorgrids,
    grid style=dashed,
    legend style={at={(0.5,-0.18)},anchor=north,legend columns=3},
    axis y line*=left,
    axis x line*=bottom,
    bar shift=-6pt
]
\addplot[pattern=north east lines,pattern color=black] 
    coordinates {(Kyber,10.65) (Dhrystone,15.3) (CoreMark,101)};
\addplot[pattern=dots,pattern color=black] 
    coordinates {(Kyber,29.3) (Dhrystone,24.7) (CoreMark,107)};
\addplot[pattern=crosshatch,pattern color=black] 
    coordinates {(Kyber,2.6) (Dhrystone,1.6) (CoreMark,1.05)};
\legend{Native time (s), Enclave time (s), Slowdown ×}
\end{axis}

% --- Right axis: Context switches ---
\begin{axis}[
    ybar,
    bar width=8pt,
    width=14cm,
    height=8cm,
    ymin=0,
    ymax=70000,
    ylabel={Involuntary Context Switches},
    symbolic x coords={Kyber,Dhrystone,CoreMark},
    xtick=data,
    enlarge x limits=0.35,
    hide x axis,
    axis y line*=right,
    axis x line=none,
    bar shift=10pt
]
\addplot[pattern=horizontal lines,pattern color=black] 
    coordinates {(Kyber,66000) (Dhrystone,66000) (CoreMark,66000)};
\legend{Involuntary CS}
\end{axis}

\end{tikzpicture}
\caption{Native vs enclave performance: absolute times, slowdown factors (left axis), and involuntary context switches (right axis).}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=12pt,
    width=12cm,
    height=7cm,
    ymin=0,
    ylabel={Value},
    symbolic x coords={RSS\ (KB), Minor\ PF, Major\ PF},
    xtick=data,
    enlarge x limits=0.25,
    ymajorgrids,
    grid style=dashed,
    legend style={at={(0.5,-0.18)},anchor=north,legend columns=-1}
]
% Native values
\addplot[pattern=north east lines,pattern color=black] coordinates
    {(RSS\ (KB),10) (Minor\ PF,1) (Major\ PF,0)};
% Enclave values
\addplot[pattern=dots,pattern color=black] coordinates
    {(RSS\ (KB),10) (Minor\ PF,1) (Major\ PF,0)};

\legend{Native, Enclave}
\end{axis}
\end{tikzpicture}
\caption{Kyber benchmark: memory usage (RSS) and page fault counts for native vs enclave execution.}
\label{fig:memory_pagefaults_chart}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}
% Left axis: CPU time percentages
\begin{axis}[
    ybar,
    bar width=8pt,
    width=14cm,
    height=8cm,
    ymin=0,
    ymax=100,
    ylabel={CPU Time (\%)},
    symbolic x coords={Kyber,Dhrystone,CoreMark},
    xtick=data,
    enlarge x limits=0.25,
    ymajorgrids,
    grid style=dashed,
    legend style={at={(0.5,-0.18)},anchor=north,legend columns=3},
    axis y line*=left,
    axis x line*=bottom
]
% User CPU% Native
\addplot[pattern=dots,pattern color=black] coordinates
    {(Kyber,95) (Dhrystone,95) (CoreMark,95)};
% User CPU% Enclave
\addplot[pattern=dots,pattern color=black!50] coordinates
    {(Kyber,95) (Dhrystone,95) (CoreMark,95)};
% System CPU% Native
\addplot[pattern=crosshatch,pattern color=black] coordinates
    {(Kyber,5) (Dhrystone,5) (CoreMark,5)};
% System CPU% Enclave
\addplot[pattern=crosshatch,pattern color=black!50] coordinates
    {(Kyber,5) (Dhrystone,5) (CoreMark,5)};

\legend{
    User CPU\% (Native),
    User CPU\% (Enclave),
    System CPU\% (Native),
    System CPU\% (Enclave),
    Ctx Switches (Native),
    Ctx Switches (Enclave)
}
\end{axis}

% Right axis: Context switches
\begin{axis}[
    ybar,
    bar width=8pt,
    width=14cm,
    height=8cm,
    ymin=0,
    ymax=70000,
    ylabel={Involuntary Context Switches},
    symbolic x coords={Kyber,Dhrystone,CoreMark},
    xtick=data,
    enlarge x limits=0.25,
    hide x axis,
    axis y line*=right,
    axis x line=none
]
% Context switches Native
\addplot[pattern=north east lines,pattern color=black] coordinates
    {(Kyber,350) (Dhrystone,350) (CoreMark,350)};
% Context switches Enclave
\addplot[pattern=north east lines,pattern color=black!50] coordinates
    {(Kyber,66000) (Dhrystone,66000) (CoreMark,66000)};
\end{axis}

\end{tikzpicture}
\caption{Native vs enclave execution: involuntary context switches (right axis) and CPU time percentages (left axis).}
\label{fig:context_switches_dualaxis}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}

% --- Left axis: Execution times ---
\begin{axis}[
    ybar,
    bar width=6pt,
    width=14cm,
    height=8cm,
    ymin=0,
    ymax=120,
    ylabel={Execution Time (s)},
    symbolic x coords={Kyber,Dhrystone,CoreMark},
    xtick=data,
    enlarge x limits=0.4,
    ymajorgrids,
    grid style=dashed,
    legend style={at={(0.5,-0.18)},anchor=north,legend columns=3},
    axis y line*=left,
    axis x line*=bottom,
    bar shift=-4pt
]
\addplot[pattern=dots,pattern color=black] 
    coordinates {(Kyber,10.7) (Dhrystone,15.3) (CoreMark,101.5)};
\addplot[pattern=dots,pattern color=black!50] 
    coordinates {(Kyber,29.2) (Dhrystone,24.7) (CoreMark,107.3)};
\legend{Native Time, Enclave Time} % only the left-axis series here
\end{axis}

% --- Right axis: Context switches ---
\begin{axis}[
    ybar,
    bar width=6pt,
    width=14cm,
    height=8cm,
    ymin=0,
    ymax=70000,
    ylabel={Involuntary Context Switches},
    symbolic x coords={Kyber,Dhrystone,CoreMark},
    xtick=data,
    enlarge x limits=0.4,
    hide x axis,
    axis y line*=right,
    axis x line=none,
    bar shift=10pt
]
\addplot[pattern=north east lines,pattern color=black] 
    coordinates {(Kyber,66000) (Dhrystone,66000) (CoreMark,66000)};
\legend{Involuntary CS} % right-axis series legend
\end{axis}

% --- Overhead factor labels ---
\begin{axis}[
    hide axis,
    width=14cm,
    height=8cm,
    symbolic x coords={Kyber,Dhrystone,CoreMark}
]
\node[font=\small, anchor=south] at (axis cs:Kyber,29.2) {2.73$\times$};
\node[font=\small, anchor=south] at (axis cs:Dhrystone,24.7) {1.61$\times$};
\node[font=\small, anchor=south] at (axis cs:CoreMark,107.3) {1.06$\times$};
\end{axis}

\end{tikzpicture}
\caption{Native vs enclave execution times (left axis) and involuntary context switches (right axis), with overhead factors above Enclave bars}
\label{fig:sensitivity-overheads-chart}
\end{figure}
